### 2018-10-21 Sections/foreword.tex
Bib errors fixed

\dropcap{Q}{uantum} technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only preexisting quantum computer scientists, but also classical computer scientists, physicists, economists, artists, musicians, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have -- the creation of the global quantum internet \cite{bib:van2014quantum, bib:Kimble2008}. We expect the answer to that question will look very different to what emerged from the classical internet.

>>>>

\dropcap{Q}{uantum} technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only preexisting quantum computer scientists, but also classical computer scientists, physicists, economists, artists, musicians, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have -- the creation of the global quantum internet \cite{bib:van2014quantum, bib:kimble2008quantum}. We expect the answer to that question will look very different to what emerged from the classical internet.

### 2018-10-21 Sections/physical_architectures_for_quantum_computing.tex
Bib errors fixed

LOQC allows universal quantum computing to be implemented using single-photon polarisation or dual-rail encoding, with only linear optics interactions, i.e beamsplitter/phase-shifter networks \cite{bib:Reck94}, with the addition of quantum memory, and fast-feedforward, whereby some photons are measured, and the remaining part of the optical circuit is dynamically reconfigured based on the measurement outcomes. The former is readily available technology today, and elementary demonstrations have been performed \cite{bib:OBrien03, bib:UniversalLOOBrien}, but the latter two have proven to be somewhat more challenging.

@@

Significant progress is being made on reconfigurable, integrated LOQC devices \cite{bib:UniversalLOOBrien}, but switching times remain orders of magnitude slower than that required for fast-feedforward. The resource overhead associated with overcoming the non-determinism of entangling gates is substantial in the original KLM proposal. But despite being improved upon by cluster state approaches, to be discussed next (Sec.~\ref{sec:CS_LO}), resource scaling remains daunting. It therefore seems most likely that certain elements from LOQC might be combined into hybrid architectures, to be discussed in detail in Sec.~\ref{sec:hybrid}.

>>>>

LOQC allows universal quantum computing to be implemented using single-photon polarisation or dual-rail encoding, with only linear optics interactions, i.e beamsplitter/phase-shifter networks \cite{bib:Reck94}, with the addition of quantum memory, and fast-feedforward, whereby some photons are measured, and the remaining part of the optical circuit is dynamically reconfigured based on the measurement outcomes. The former is readily available technology today, and elementary demonstrations have been performed \cite{bib:OBrien03, bib:carolan2015universal}, but the latter two have proven to be somewhat more challenging.

@@

Significant progress is being made on reconfigurable, integrated LOQC devices \cite{bib:carolan2015universal}, but switching times remain orders of magnitude slower than that required for fast-feedforward. The resource overhead associated with overcoming the non-determinism of entangling gates is substantial in the original KLM proposal. But despite being improved upon by cluster state approaches, to be discussed next (Sec.~\ref{sec:CS_LO}), resource scaling remains daunting. It therefore seems most likely that certain elements from LOQC might be combined into hybrid architectures, to be discussed in detail in Sec.~\ref{sec:hybrid}.

### 2018-10-21 Sections/protocols_for_the_quantum_internet.tex
Bib errors fixed

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{LO_archs_long}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:UniversalLOOBrien}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{LO_archs}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:UniversalLOOBrien}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure*}
\fi

>>>>

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{LO_archs_long}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{LO_archs}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure*}
\fi

### 2018-10-21 Sections/quantum_repeater_networks.tex
Adding image cropping
Bib errors fixed

\textit{Quantum repeaters}\index{Quantum repeaters} \cite{bib:Gisin2007, bib:SSRG09, bib:WJM2015} are devices that allow high-quality entanglement to be shared between distant nodes, when no direct line of communication is available from a server to its two clients. This is achieved by dividing long-distance links into a finite number of segments interspersed with repeaters (see Fig.~\ref{fig:repeaters_1}).

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{repeaters_1}
\captionspacefig \caption{(a) Schematic representation of an entangled Bell pair $| \Psi\rangle_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{repeaters_2}
\captionspacefig \caption{Basic operation of a (first-generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure}

@@

Probably the most important operation for any quantum repeater setup is entanglement distribution, the process of creating entanglement between two remote parties (Alice and Bob) connected by a quantum channel (generally an optical fibre or free-space link). This can be implemented in a number of ways \cite{bib:Bennett96, bib:enk98, bib:bennett93, bib:SSRG09, bib:childress06, bib:loock06, bib:munro08}, but can be broadly categorised into three basic schemas:
\begin{itemize}
\item Photon emission from quantum memories in the repeater nodes, followed by which-path erasure.\index{Which-path erasure}
\item Absorption of entangled photons by quantum memories.
\item Photon emission at one node and absorption at another.
\end{itemize}
By far, the emission based schemes are the most common, which we will concentrate on here. Such schemes operate by using an entangling operation -- \textit{which-path erasure} -- to entangle two quantum memories via photons to which they were coupled. Effectively the process teleports the action of an entangling gate\index{Quantum gate teleportation} (Sec.~\ref{sec:teleport_gate}) acting on the photons onto the quantum memories to which they were entangled.

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{repeaters_3}
\captionspacefig \caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitters}\index{Polarising beamsplitters} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{repeaters_4}
\captionspacefig \caption{Entanglement purification: (a) The simplest purification scheme involving two pairs of shared remote entangled quantum memories (\mbox{$A_1-B_1$} and \mbox{$A_2-B_2$}). The purification operation begins with Alice performing a CNOT operation between memories $A_1$ and $B_1$. Similarly Bob performs a CNOT operation between his memories. Alice and Bob then measure qubits $A_2$ and $B_2$ in the computational ($0$, $1$) basis and share their results. They discard the resulting state if between them they measured odd parity ($0,1$ or $1,0$). They keep the state if they measured an even parity between them ($0,0$ or $1,1$) which should have higher fidelity. (b) Two qubits are removed, leaving a residual two-qubit state between $A_1$ and $B_1$ with improved fidelity.} 
\label{fig:repeaters_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{repeaters_5}
\captionspacefig \caption{Plot of the increased fidelity and success probability for entanglement purification for a mixture of two Bell states with initial fidelity $F$. The dashed lines show how multiple pairs with an initial fidelity $F=0.7$ can be purified iteratively to a final fidelity above 0.95.} 
\label{fig:rep_purification}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{repeaters_6}
\captionspacefig \caption{Entanglement swapping: (a) An entangled state is shared between Alice and a repeater station ($A_1-A_2$), and also between the repeater station and Bob ($B_2-B_1$). The entanglement operation begins by performing a Bell state measurement between $A_2$ and $B_2$ using a CNOT gate, and measurements at $D_1$, $D_2$.  The measurements indicate which Bell state we have projected our state $A_1$, $B_1$ onto. (b) The resultant entangled state between $A_1$, $B_1$ with the qubits $A_2$ and $B_2$ disentangled from it.}
\label{fig:repeaters_6}
\end{figure}

@@

Now it's straightforward, albeit tedious, to show that $T_{n,k,L_\mathrm{tot}}$ is given by \cite{bib:braztzik2013},
\begin{widetext}
\begin{align*}
 T_{n,k,L_\mathrm{tot}} &\sim \frac{3^n}{2^{n-1} p_\mathrm{ED}} \prod_{i=0}^{n-1} \left(\frac{3}{2}\right)^{k}  \frac{1}{P_\mathrm{ES}(n-i)  }\prod_{j=0}^{k-1} \frac{1}{p_\mathrm{P}(k-j,n-i)}  \nonumber \\
 &+\sum_{m=1}^n\left(\frac{3^{n-m}}{2^{n-1}}\right) \prod_{i=0}^{n-m}   \left(\frac{3}{2}\right)^{k} \frac{1}{P_\mathrm{ES}(n-i)}  \prod_{j=0}^{k-1}  \frac{1}{p_\mathrm{P}(k-j,n-i)}  \\
&+\sum_{m=1}^n {\sum_{q=0}^{k-1} \left(\frac{3^{n-m+q}}{2^{n- 2 m+q}}\right) \prod_{r=0}^{q}\frac{1}{p_\mathrm{P}(k-r,m)}} 
\prod_{i=0}^{n-m-1}   \left(\frac{3}{2}\right)^{k} \frac{1}{P_\mathrm{ES}(n-i)}  \prod_{j=0}^{k-1}  \frac{1}{p_\mathrm{P}(k-j,n-i)} \nonumber 
\end{align*}
\end{widetext}
where $p_\mathrm{ED}$ is the probability of successfully distributing entanglement between adjacent repeater nodes, while $p_\mathrm{P}(j,i)$ [$p_\mathrm{ES}(i)$] represents the purification [entanglement swapping] probability at the $i$th nesting level with $j$ rounds of purification. The factors of $3/2$ present in all entanglement distribution, purification and swapping operations is a multiplicative factor associated with the extra time required for the two pairs to be available for the various quantum operations \cite{bib:SSRG09}.

@@

\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{repeaters_7}
\captionspacefig \caption{Purification circuit based on quantum error correction. The specific example shown is for the \mbox{[[5,1,3]]} code \cite{bib:Bennettr1996a, bib:Knill97}. We assume that entanglement distribution has allowed Alice and Bob to create 5 copies of their imperfect Bell pairs. The error correction circuit is executed independently between the two nodes. While we show the situation when the measurements at both sides are done directly on four pairs of entangled qubits (leaving us with one unencoded Bell pair), one can also use ancilla qubits to measure the appropriate syndromes. As soon as the measurements are complete both nodes' qubits are available for continued use as the error correction is deterministic and there are no failure events that need to be heralded. In this case the classical message between nodes just carries Alice's measurement results, allowing either node to interpret which Bell state was generated and for one of them to apply the bit-flip or phase-flip correction operation if needed to recover the desired Bell state. In many cases this correction is classically tracked in the Pauli frame, which keeps a record of whether $\hat{X}$ and/or $\hat{Z}$ corrections need to be performed at some stage \cite{bib:jiang09, bib:munro10}. Note that it's not necessary to measure out all but one of the qubits involved in the entangled links. Instead the logical qubit can be maintained by the use of ancilla qubits within that node with the syndrome being measured with the help of the ancilla qubits. Entanglement swapping could then be performed on the logical qubits enabling a much more error resilient system.
}
\label{fig:repeaters_7}
\end{figure*}

@@

\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{repeaters_8}
\captionspacefig \caption{A butterfly design quantum repeater network protocol that reduces the requirements on all the quantum memory times to only that associated with the signalling time between adjacent repeater nodes \cite{bib:munro10}. Enough pairs must be generated between the node to ensure that we can use them in the error correction code in a single round trip time between adjacent nodes. The scheme relies on multiple entangled pairs being generated temporally, starting from the mid point of the network. The protocol begins with the central node creating links to both the left and right nearest neighbour nodes in sufficient number to allow an error correction code to be implemented. Once they are created the error correction circuits are applied to the links left and right of this central node (effectively creating encoded logical links). Entanglement swapping at the middle node is then applied  between these logical links, creating a logical link between the left and right adjacent nodes. The left and right nodes can then do the same to their next adjacent repeater nodes, error correcting as they go, until the desired end-to-end entangled link is achieved.}
\label{fig:repeaters_8}
\end{figure*}

@@

The use of error correcting codes significantly improves the performance of second-generation quantum repeaters compared to first-generation ones. The second-generation schemes are now limited by the communication time between adjacent repeater nodes to herald whether entanglement distribution was successful or not \cite{bib:munro10, bib:munro12}. The communication (both quantum and classical) is ultimately limited by the speed of light (either in fibre or over free space). The natural question is whether we can improve performance even further.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{repeaters_9}
\captionspacefig \caption{Transmission of a quantum signal using loss-based error correction codes in a quantum network.}\label{fig:repeaters_9}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{racetime}
\captionspacefig \caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time conditions} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure}

>>>>

\textit{Quantum repeaters}\index{Quantum repeaters} \cite{bib:Gisin2007, bib:sangouard11, bib:WJM2015} are devices that allow high-quality entanglement to be shared between distant nodes, when no direct line of communication is available from a server to its two clients. This is achieved by dividing long-distance links into a finite number of segments interspersed with repeaters (see Fig.~\ref{fig:repeaters_1}).

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{repeaters_1}
\captionspacefig \caption{(a) Schematic representation of an entangled Bell pair $| \Psi\rangle_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{repeaters_2}
\captionspacefig \caption{Basic operation of a (first-generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure}

@@

Probably the most important operation for any quantum repeater setup is entanglement distribution, the process of creating entanglement between two remote parties (Alice and Bob) connected by a quantum channel (generally an optical fibre or free-space link). This can be implemented in a number of ways \cite{bib:Bennett96, bib:enk98, bib:bennett93, bib:sangouard11, bib:childress06, bib:loock06, bib:munro08}, but can be broadly categorised into three basic schemas:
\begin{itemize}
\item Photon emission from quantum memories in the repeater nodes, followed by which-path erasure.\index{Which-path erasure}
\item Absorption of entangled photons by quantum memories.
\item Photon emission at one node and absorption at another.
\end{itemize}
By far, the emission based schemes are the most common, which we will concentrate on here. Such schemes operate by using an entangling operation -- \textit{which-path erasure} -- to entangle two quantum memories via photons to which they were coupled. Effectively the process teleports the action of an entangling gate\index{Quantum gate teleportation} (Sec.~\ref{sec:teleport_gate}) acting on the photons onto the quantum memories to which they were entangled.

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{repeaters_3}
\captionspacefig \caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitters}\index{Polarising beamsplitters} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{repeaters_4}
\captionspacefig \caption{Entanglement purification: (a) The simplest purification scheme involving two pairs of shared remote entangled quantum memories (\mbox{$A_1-B_1$} and \mbox{$A_2-B_2$}). The purification operation begins with Alice performing a CNOT operation between memories $A_1$ and $B_1$. Similarly Bob performs a CNOT operation between his memories. Alice and Bob then measure qubits $A_2$ and $B_2$ in the computational ($0$, $1$) basis and share their results. They discard the resulting state if between them they measured odd parity ($0,1$ or $1,0$). They keep the state if they measured an even parity between them ($0,0$ or $1,1$) which should have higher fidelity. (b) Two qubits are removed, leaving a residual two-qubit state between $A_1$ and $B_1$ with improved fidelity.} 
\label{fig:repeaters_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{repeaters_5}
\captionspacefig \caption{Plot of the increased fidelity and success probability for entanglement purification for a mixture of two Bell states with initial fidelity $F$. The dashed lines show how multiple pairs with an initial fidelity $F=0.7$ can be purified iteratively to a final fidelity above 0.95.} 
\label{fig:rep_purification}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{repeaters_6}
\captionspacefig \caption{Entanglement swapping: (a) An entangled state is shared between Alice and a repeater station ($A_1-A_2$), and also between the repeater station and Bob ($B_2-B_1$). The entanglement operation begins by performing a Bell state measurement between $A_2$ and $B_2$ using a CNOT gate, and measurements at $D_1$, $D_2$.  The measurements indicate which Bell state we have projected our state $A_1$, $B_1$ onto. (b) The resultant entangled state between $A_1$, $B_1$ with the qubits $A_2$ and $B_2$ disentangled from it.}
\label{fig:repeaters_6}
\end{figure}

@@

Now it's straightforward, albeit tedious, to show that $T_{n,k,L_\mathrm{tot}}$ is given by \cite{bib:braztzik2013},
\begin{widetext}
\begin{align*}
 T_{n,k,L_\mathrm{tot}} &\sim \frac{3^n}{2^{n-1} p_\mathrm{ED}} \prod_{i=0}^{n-1} \left(\frac{3}{2}\right)^{k}  \frac{1}{P_\mathrm{ES}(n-i)  }\prod_{j=0}^{k-1} \frac{1}{p_\mathrm{P}(k-j,n-i)}  \nonumber \\
 &+\sum_{m=1}^n\left(\frac{3^{n-m}}{2^{n-1}}\right) \prod_{i=0}^{n-m}   \left(\frac{3}{2}\right)^{k} \frac{1}{P_\mathrm{ES}(n-i)}  \prod_{j=0}^{k-1}  \frac{1}{p_\mathrm{P}(k-j,n-i)}  \\
&+\sum_{m=1}^n {\sum_{q=0}^{k-1} \left(\frac{3^{n-m+q}}{2^{n- 2 m+q}}\right) \prod_{r=0}^{q}\frac{1}{p_\mathrm{P}(k-r,m)}} 
\prod_{i=0}^{n-m-1}   \left(\frac{3}{2}\right)^{k} \frac{1}{P_\mathrm{ES}(n-i)}  \prod_{j=0}^{k-1}  \frac{1}{p_\mathrm{P}(k-j,n-i)} \nonumber 
\end{align*}
\end{widetext}
where $p_\mathrm{ED}$ is the probability of successfully distributing entanglement between adjacent repeater nodes, while $p_\mathrm{P}(j,i)$ [$p_\mathrm{ES}(i)$] represents the purification [entanglement swapping] probability at the $i$th nesting level with $j$ rounds of purification. The factors of $3/2$ present in all entanglement distribution, purification and swapping operations is a multiplicative factor associated with the extra time required for the two pairs to be available for the various quantum operations \cite{bib:sangouard11}.

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{repeaters_7}
\captionspacefig \caption{Purification circuit based on quantum error correction. The specific example shown is for the \mbox{[[5,1,3]]} code \cite{bib:Bennettr1996a, bib:Knill97}. We assume that entanglement distribution has allowed Alice and Bob to create 5 copies of their imperfect Bell pairs. The error correction circuit is executed independently between the two nodes. While we show the situation when the measurements at both sides are done directly on four pairs of entangled qubits (leaving us with one unencoded Bell pair), one can also use ancilla qubits to measure the appropriate syndromes. As soon as the measurements are complete both nodes' qubits are available for continued use as the error correction is deterministic and there are no failure events that need to be heralded. In this case the classical message between nodes just carries Alice's measurement results, allowing either node to interpret which Bell state was generated and for one of them to apply the bit-flip or phase-flip correction operation if needed to recover the desired Bell state. In many cases this correction is classically tracked in the Pauli frame, which keeps a record of whether $\hat{X}$ and/or $\hat{Z}$ corrections need to be performed at some stage \cite{bib:jiang09, bib:munro10}. Note that it's not necessary to measure out all but one of the qubits involved in the entangled links. Instead the logical qubit can be maintained by the use of ancilla qubits within that node with the syndrome being measured with the help of the ancilla qubits. Entanglement swapping could then be performed on the logical qubits enabling a much more error resilient system.
}
\label{fig:repeaters_7}
\end{figure*}

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{repeaters_8}
\captionspacefig \caption{A butterfly design quantum repeater network protocol that reduces the requirements on all the quantum memory times to only that associated with the signalling time between adjacent repeater nodes \cite{bib:munro10}. Enough pairs must be generated between the node to ensure that we can use them in the error correction code in a single round trip time between adjacent nodes. The scheme relies on multiple entangled pairs being generated temporally, starting from the mid point of the network. The protocol begins with the central node creating links to both the left and right nearest neighbour nodes in sufficient number to allow an error correction code to be implemented. Once they are created the error correction circuits are applied to the links left and right of this central node (effectively creating encoded logical links). Entanglement swapping at the middle node is then applied  between these logical links, creating a logical link between the left and right adjacent nodes. The left and right nodes can then do the same to their next adjacent repeater nodes, error correcting as they go, until the desired end-to-end entangled link is achieved.}
\label{fig:repeaters_8}
\end{figure*}

@@

The use of error correcting codes significantly improves the performance of second-generation quantum repeaters compared to first-generation ones. The second-generation schemes are now limited by the communication time between adjacent repeater nodes to herald whether entanglement distribution was successful or not \cite{bib:munro10, bib:munro12}. The communication (both quantum and classical) is ultimately limited by the speed of light (either in fibre or over free-space). The natural question is whether we can improve performance even further.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{repeaters_9}
\captionspacefig \caption{Transmission of a quantum signal using loss-based error correction codes in a quantum network.}\label{fig:repeaters_9}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{racetime}
\captionspacefig \caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time conditions} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure}
